### 2020-04-09 rR.tex
started writing

% Created by tikzDevice version 0.12.3 on 2020-04-09 01:19:07
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

@@

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 35.86,249.99) --
	( 38.99,250.83) --
	( 42.13,251.68) --
	( 45.26,252.56) --
	( 48.40,253.45) --
	( 51.53,254.37) --
	( 54.67,255.30) --
	( 57.81,256.26) --
	( 60.94,257.23) --
	( 64.08,258.23) --
	( 67.21,259.24) --
	( 70.35,260.28) --
	( 73.48,261.33) --
	( 76.62,262.40) --
	( 79.76,263.50) --
	( 82.89,264.61) --
	( 86.03,265.75) --
	( 89.16,266.90) --
	( 92.30,268.08) --
	( 95.43,269.28) --
	( 98.57,270.49) --
	(101.71,271.73) --
	(104.84,272.98) --
	(107.98,274.24) --
	(111.11,275.53) --
	(114.25,276.84) --
	(117.39,278.17) --
	(120.52,279.52) --
	(123.66,280.90) --
	(126.79,282.30) --
	(129.93,283.73) --
	(133.06,285.18) --
	(136.20,286.64) --
	(139.34,288.13) --
	(142.47,289.63) --
	(145.61,291.16) --
	(148.74,292.71) --
	(151.88,294.29) --
	(155.01,295.91) --
	(158.15,297.56) --
	(161.29,299.22) --
	(164.42,300.90) --
	(167.56,302.61) --
	(170.69,304.34) --
	(173.83,306.09) --
	(176.96,307.87) --
	(180.10,309.69) --
	(183.24,311.54) --
	(186.37,313.42) --
	(189.51,315.35) --
	(192.64,317.30) --
	(195.78,319.28) --
	(198.91,321.29) --
	(202.05,323.33) --
	(205.19,325.39) --
	(208.32,327.49) --
	(211.46,329.62) --
	(214.59,331.79) --
	(217.73,334.00) --
	(220.86,336.24) --
	(224.00,338.53) --
	(227.14,340.85) --
	(230.27,343.21) --
	(233.41,345.59) --
	(236.54,348.02) --
	(239.68,350.47) --
	(242.82,352.96) --
	(245.95,355.49) --
	(249.09,358.05) --
	(252.22,360.64) --
	(255.36,363.27) --
	(258.49,365.94) --
	(261.63,368.64) --
	(264.77,371.37) --
	(267.90,374.15) --
	(271.04,376.95) --
	(274.17,379.79) --
	(277.31,382.67) --
	(280.44,385.58) --
	(283.58,388.52);
\definecolor{drawColor}{RGB}{230,159,0}

\path[draw=drawColor,line width= 1.1pt,dash pattern=on 2pt off 2pt ,line join=round] ( 35.86,249.94) --
	( 38.99,250.75) --
	( 42.13,251.59) --
	( 45.26,252.45) --
	( 48.40,253.32) --
	( 51.53,254.22) --
	( 54.67,255.14) --
	( 57.81,256.08) --
	( 60.94,257.04) --
	( 64.08,258.02) --
	( 67.21,259.02) --
	( 70.35,260.04) --
	( 73.48,261.08) --
	( 76.62,262.14) --
	( 79.76,263.22) --
	( 82.89,264.33) --
	( 86.03,265.45) --
	( 89.16,266.60) --
	( 92.30,267.77) --
	( 95.43,268.96) --
	( 98.57,270.16) --
	(101.71,271.39) --
	(104.84,272.63) --
	(107.98,273.89) --
	(111.11,275.17) --
	(114.25,276.47) --
	(117.39,277.79) --
	(120.52,279.14) --
	(123.66,280.51) --
	(126.79,281.91) --
	(129.93,283.34) --
	(133.06,284.79) --
	(136.20,286.25) --
	(139.34,287.72) --
	(142.47,289.22) --
	(145.61,290.74) --
	(148.74,292.29) --
	(151.88,293.88) --
	(155.01,295.51) --
	(158.15,297.16) --
	(161.29,298.84) --
	(164.42,300.53) --
	(167.56,302.25) --
	(170.69,303.99) --
	(173.83,305.76) --
	(176.96,307.57) --
	(180.10,309.41) --
	(183.24,311.28) --
	(186.37,313.20) --
	(189.51,315.16) --
	(192.64,317.16) --
	(195.78,319.19) --
	(198.91,321.24) --
	(202.05,323.33) --
	(205.19,325.45) --
	(208.32,327.61) --
	(211.46,329.80) --
	(214.59,332.03) --
	(217.73,334.31) --
	(220.86,336.63) --
	(224.00,339.00) --
	(227.14,341.41) --
	(230.27,343.86) --
	(233.41,346.34) --
	(236.54,348.86) --
	(239.68,351.42) --
	(242.82,354.02) --
	(245.95,356.66) --
	(249.09,359.33) --
	(252.22,362.05) --
	(255.36,364.80) --
	(258.49,367.59) --
	(261.63,370.43) --
	(264.77,373.30) --
	(267.90,376.22) --
	(271.04,379.17) --
	(274.17,382.16) --
	(277.31,385.19) --
	(280.44,388.26) --
	(283.58,391.37);
\definecolor{drawColor}{RGB}{86,180,233}

\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 2pt ,line join=round] ( 35.86,249.92) --
	( 38.99,250.73) --
	( 42.13,251.56) --
	( 45.26,252.41) --
	( 48.40,253.28) --
	( 51.53,254.17) --
	( 54.67,255.09) --
	( 57.81,256.02) --
	( 60.94,256.97) --
	( 64.08,257.95) --
	( 67.21,258.94) --
	( 70.35,259.96) --
	( 73.48,260.99) --
	( 76.62,262.05) --
	( 79.76,263.13) --
	( 82.89,264.23) --
	( 86.03,265.35) --
	( 89.16,266.49) --
	( 92.30,267.65) --
	( 95.43,268.84) --
	( 98.57,270.04) --
	(101.71,271.26) --
	(104.84,272.50) --
	(107.98,273.76) --
	(111.11,275.03) --
	(114.25,276.33) --
	(117.39,277.65) --
	(120.52,279.00) --
	(123.66,280.37) --
	(126.79,281.76) --
	(129.93,283.19) --
	(133.06,284.64) --
	(136.20,286.09) --
	(139.34,287.56) --
	(142.47,289.06) --
	(145.61,290.58) --
	(148.74,292.13) --
	(151.88,293.72) --
	(155.01,295.35) --
	(158.15,297.01) --
	(161.29,298.68) --
	(164.42,300.38) --
	(167.56,302.10) --
	(170.69,303.84) --
	(173.83,305.62) --
	(176.96,307.42) --
	(180.10,309.27) --
	(183.24,311.15) --
	(186.37,313.08) --
	(189.51,315.05) --
	(192.64,317.07) --
	(195.78,319.11) --
	(198.91,321.18) --
	(202.05,323.28) --
	(205.19,325.42) --
	(208.32,327.59) --
	(211.46,329.81) --
	(214.59,332.07) --
	(217.73,334.37) --
	(220.86,336.72) --
	(224.00,339.12) --
	(227.14,341.56) --
	(230.27,344.04) --
	(233.41,346.57) --
	(236.54,349.13) --
	(239.68,351.73) --
	(242.82,354.37) --
	(245.95,357.05) --
	(249.09,359.77) --
	(252.22,362.53) --
	(255.36,365.34) --
	(258.49,368.19) --
	(261.63,371.07) --
	(264.77,374.01) --
	(267.90,376.98) --
	(271.04,379.99) --
	(274.17,383.04) --
	(277.31,386.14) --
	(280.44,389.27) --
	(283.58,392.45);
\definecolor{drawColor}{RGB}{0,158,115}

\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 4pt ,line join=round] ( 35.86,249.92) --
	( 38.99,250.74) --
	( 42.13,251.58) --
	( 45.26,252.44) --
	( 48.40,253.32) --
	( 51.53,254.22) --
	( 54.67,255.14) --
	( 57.81,256.08) --
	( 60.94,257.05) --
	( 64.08,258.03) --
	( 67.21,259.03) --
	( 70.35,260.05) --
	( 73.48,261.10) --
	( 76.62,262.16) --
	( 79.76,263.24) --
	( 82.89,264.35) --
	( 86.03,265.47) --
	( 89.16,266.62) --
	( 92.30,267.79) --
	( 95.43,268.98) --
	( 98.57,270.19) --
	(101.71,271.41) --
	(104.84,272.65) --
	(107.98,273.91) --
	(111.11,275.19) --
	(114.25,276.49) --
	(117.39,277.81) --
	(120.52,279.16) --
	(123.66,280.53) --
	(126.79,281.93) --
	(129.93,283.35) --
	(133.06,284.80) --
	(136.20,286.25) --
	(139.34,287.72) --
	(142.47,289.22) --
	(145.61,290.73) --
	(148.74,292.28) --
	(151.88,293.87) --
	(155.01,295.49) --
	(158.15,297.14) --
	(161.29,298.82) --
	(164.42,300.51) --
	(167.56,302.22) --
	(170.69,303.95) --
	(173.83,305.72) --
	(176.96,307.52) --
	(180.10,309.35) --
	(183.24,311.23) --
	(186.37,313.14) --
	(189.51,315.11) --
	(192.64,317.11) --
	(195.78,319.14) --
	(198.91,321.20) --
	(202.05,323.29) --
	(205.19,325.41) --
	(208.32,327.58) --
	(211.46,329.78) --
	(214.59,332.02) --
	(217.73,334.31) --
	(220.86,336.64) --
	(224.00,339.03) --
	(227.14,341.45) --
	(230.27,343.92) --
	(233.41,346.42) --
	(236.54,348.96) --
	(239.68,351.54) --
	(242.82,354.16) --
	(245.95,356.82) --
	(249.09,359.52) --
	(252.22,362.27) --
	(255.36,365.05) --
	(258.49,367.87) --
	(261.63,370.74) --
	(264.77,373.64) --
	(267.90,376.59) --
	(271.04,379.58) --
	(274.17,382.60) --
	(277.31,385.67) --
	(280.44,388.78) --
	(283.58,391.93);
\definecolor{fillColor}{RGB}{230,159,0}

\path[fill=fillColor] ( 35.86,253.66) --
	( 39.22,247.84) --
	( 32.49,247.84) --
	cycle;

\path[fill=fillColor] ( 44.40,256.05) --
	( 47.76,250.22) --
	( 41.03,250.22) --
	cycle;

\path[fill=fillColor] ( 52.94,258.56) --
	( 56.30,252.73) --
	( 49.58,252.73) --
	cycle;

\path[fill=fillColor] ( 61.48,261.19) --
	( 64.85,255.36) --
	( 58.12,255.36) --
	cycle;

\path[fill=fillColor] ( 70.02,263.94) --
	( 73.39,258.11) --
	( 66.66,258.11) --
	cycle;

\path[fill=fillColor] ( 78.57,266.81) --
	( 81.93,260.99) --
	( 75.20,260.99) --
	cycle;

\path[fill=fillColor] ( 87.11,269.83) --
	( 90.47,264.01) --
	( 83.75,264.01) --
	cycle;

\path[fill=fillColor] ( 95.65,273.00) --
	( 99.01,267.18) --
	( 92.29,267.18) --
	cycle;

\path[fill=fillColor] (104.19,276.33) --
	(107.56,270.51) --
	(100.83,270.51) --
	cycle;

\path[fill=fillColor] (112.74,279.79) --
	(116.10,273.97) --
	(109.37,273.97) --
	cycle;

\path[fill=fillColor] (121.28,283.41) --
	(124.64,277.58) --
	(117.91,277.58) --
	cycle;

\path[fill=fillColor] (129.82,287.19) --
	(133.18,281.36) --
	(126.46,281.36) --
	cycle;

\path[fill=fillColor] (138.36,291.15) --
	(141.73,285.33) --
	(135.00,285.33) --
	cycle;

\path[fill=fillColor] (146.90,295.31) --
	(150.27,289.49) --
	(143.54,289.49) --
	cycle;

\path[fill=fillColor] (155.45,299.62) --
	(158.81,293.80) --
	(152.08,293.80) --
	cycle;

\path[fill=fillColor] (163.99,304.14) --
	(167.35,298.31) --
	(160.63,298.31) --
	cycle;

\path[fill=fillColor] (172.53,308.85) --
	(175.89,303.03) --
	(169.17,303.03) --
	cycle;

\path[fill=fillColor] (181.07,313.93) --
	(184.44,308.10) --
	(177.71,308.10) --
	cycle;

\path[fill=fillColor] (189.62,319.15) --
	(192.98,313.32) --
	(186.25,313.32) --
	cycle;

\path[fill=fillColor] (198.16,324.63) --
	(201.52,318.80) --
	(194.79,318.80) --
	cycle;

\path[fill=fillColor] (206.70,330.30) --
	(210.06,324.48) --
	(203.34,324.48) --
	cycle;

\path[fill=fillColor] (215.24,336.32) --
	(218.61,330.49) --
	(211.88,330.49) --
	cycle;

\path[fill=fillColor] (223.78,342.61) --
	(227.15,336.78) --
	(220.42,336.78) --
	cycle;

\path[fill=fillColor] (232.33,349.11) --
	(235.69,343.29) --
	(228.96,343.29) --
	cycle;

\path[fill=fillColor] (240.87,356.01) --
	(244.23,350.19) --
	(237.51,350.19) --
	cycle;

\path[fill=fillColor] (249.41,363.19) --
	(252.77,357.37) --
	(246.05,357.37) --
	cycle;

\path[fill=fillColor] (257.95,370.87) --
	(261.32,365.04) --
	(254.59,365.04) --
	cycle;

\path[fill=fillColor] (266.50,378.77) --
	(269.86,372.95) --
	(263.13,372.95) --
	cycle;

\path[fill=fillColor] (275.04,386.88) --
	(278.40,381.05) --
	(271.67,381.05) --
	cycle;

\path[fill=fillColor] (283.58,395.60) --
	(286.94,389.77) --
	(280.22,389.77) --
	cycle;
\definecolor{fillColor}{RGB}{86,180,233}

\path[fill=fillColor] ( 33.36,247.26) --
	( 38.35,247.26) --
	( 38.35,252.26) --
	( 33.36,252.26) --
	cycle;

\path[fill=fillColor] ( 41.90,249.63) --
	( 46.90,249.63) --
	( 46.90,254.63) --
	( 41.90,254.63) --
	cycle;

\path[fill=fillColor] ( 50.44,252.12) --
	( 55.44,252.12) --
	( 55.44,257.12) --
	( 50.44,257.12) --
	cycle;

\path[fill=fillColor] ( 58.98,254.74) --
	( 63.98,254.74) --
	( 63.98,259.73) --
	( 58.98,259.73) --
	cycle;

\path[fill=fillColor] ( 67.53,257.47) --
	( 72.52,257.47) --
	( 72.52,262.47) --
	( 67.53,262.47) --
	cycle;

\path[fill=fillColor] ( 76.07,260.33) --
	( 81.06,260.33) --
	( 81.06,265.33) --
	( 76.07,265.33) --
	cycle;

\path[fill=fillColor] ( 84.61,263.34) --
	( 89.61,263.34) --
	( 89.61,268.34) --
	( 84.61,268.34) --
	cycle;

\path[fill=fillColor] ( 93.15,266.51) --
	( 98.15,266.51) --
	( 98.15,271.50) --
	( 93.15,271.50) --
	cycle;

\path[fill=fillColor] (101.70,269.84) --
	(106.69,269.84) --
	(106.69,274.83) --
	(101.70,274.83) --
	cycle;

\path[fill=fillColor] (110.24,273.29) --
	(115.23,273.29) --
	(115.23,278.28) --
	(110.24,278.28) --
	cycle;

\path[fill=fillColor] (118.78,276.89) --
	(123.78,276.89) --
	(123.78,281.88) --
	(118.78,281.88) --
	cycle;

\path[fill=fillColor] (127.32,280.66) --
	(132.32,280.66) --
	(132.32,285.65) --
	(127.32,285.65) --
	cycle;

\path[fill=fillColor] (135.86,284.62) --
	(140.86,284.62) --
	(140.86,289.62) --
	(135.86,289.62) --
	cycle;

\path[fill=fillColor] (144.41,288.79) --
	(149.40,288.79) --
	(149.40,293.79) --
	(144.41,293.79) --
	cycle;

\path[fill=fillColor] (152.95,293.08) --
	(157.94,293.08) --
	(157.94,298.08) --
	(152.95,298.08) --
	cycle;

\path[fill=fillColor] (161.49,297.59) --
	(166.49,297.59) --
	(166.49,302.58) --
	(161.49,302.58) --
	cycle;

\path[fill=fillColor] (170.03,302.29) --
	(175.03,302.29) --
	(175.03,307.29) --
	(170.03,307.29) --
	cycle;

\path[fill=fillColor] (178.58,307.43) --
	(183.57,307.43) --
	(183.57,312.42) --
	(178.58,312.42) --
	cycle;

\path[fill=fillColor] (187.12,312.67) --
	(192.11,312.67) --
	(192.11,317.67) --
	(187.12,317.67) --
	cycle;

\path[fill=fillColor] (195.66,318.20) --
	(200.66,318.20) --
	(200.66,323.19) --
	(195.66,323.19) --
	cycle;

\path[fill=fillColor] (204.20,323.88) --
	(209.20,323.88) --
	(209.20,328.88) --
	(204.20,328.88) --
	cycle;

\path[fill=fillColor] (212.74,329.97) --
	(217.74,329.97) --
	(217.74,334.96) --
	(212.74,334.96) --
	cycle;

\path[fill=fillColor] (221.29,336.33) --
	(226.28,336.33) --
	(226.28,341.33) --
	(221.29,341.33) --
	cycle;

\path[fill=fillColor] (229.83,342.88) --
	(234.82,342.88) --
	(234.82,347.87) --
	(229.83,347.87) --
	cycle;

\path[fill=fillColor] (238.37,349.88) --
	(243.37,349.88) --
	(243.37,354.88) --
	(238.37,354.88) --
	cycle;

>>>>

% Created by tikzDevice version 0.12.3 on 2020-04-09 18:48:49
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

@@

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 27.31,247.68) --
	( 30.56,248.50) --
	( 33.80,249.34) --
	( 37.04,250.20) --
	( 40.29,251.09) --
	( 43.53,251.99) --
	( 46.78,252.92) --
	( 50.02,253.86) --
	( 53.26,254.83) --
	( 56.51,255.81) --
	( 59.75,256.82) --
	( 63.00,257.85) --
	( 66.24,258.90) --
	( 69.48,259.97) --
	( 72.73,261.06) --
	( 75.97,262.17) --
	( 79.22,263.30) --
	( 82.46,264.46) --
	( 85.70,265.64) --
	( 88.95,266.84) --
	( 92.19,268.05) --
	( 95.43,269.29) --
	( 98.68,270.54) --
	(101.92,271.81) --
	(105.17,273.11) --
	(108.41,274.42) --
	(111.65,275.76) --
	(114.90,277.13) --
	(118.14,278.52) --
	(121.39,279.93) --
	(124.63,281.37) --
	(127.87,282.82) --
	(131.12,284.29) --
	(134.36,285.79) --
	(137.61,287.30) --
	(140.85,288.84) --
	(144.09,290.41) --
	(147.34,292.01) --
	(150.58,293.64) --
	(153.82,295.30) --
	(157.07,296.99) --
	(160.31,298.71) --
	(163.56,300.44) --
	(166.80,302.19) --
	(170.04,303.97) --
	(173.29,305.78) --
	(176.53,307.62) --
	(179.78,309.49) --
	(183.02,311.40) --
	(186.26,313.35) --
	(189.51,315.33) --
	(192.75,317.36) --
	(196.00,319.41) --
	(199.24,321.50) --
	(202.48,323.61) --
	(205.73,325.76) --
	(208.97,327.95) --
	(212.21,330.17) --
	(215.46,332.42) --
	(218.70,334.72) --
	(221.95,337.06) --
	(225.19,339.44) --
	(228.43,341.86) --
	(231.68,344.31) --
	(234.92,346.79) --
	(238.17,349.31) --
	(241.41,351.87) --
	(244.65,354.47) --
	(247.90,357.09) --
	(251.14,359.76) --
	(254.39,362.46) --
	(257.63,365.21) --
	(260.87,367.98) --
	(264.12,370.80) --
	(267.36,373.65) --
	(270.60,376.54) --
	(273.85,379.47) --
	(277.09,382.43) --
	(280.34,385.43) --
	(283.58,388.46);
\definecolor{drawColor}{RGB}{230,159,0}

\path[draw=drawColor,line width= 1.1pt,dash pattern=on 2pt off 2pt ,line join=round] ( 27.31,247.65) --
	( 30.56,248.48) --
	( 33.80,249.33) --
	( 37.04,250.20) --
	( 40.29,251.09) --
	( 43.53,252.00) --
	( 46.78,252.94) --
	( 50.02,253.89) --
	( 53.26,254.86) --
	( 56.51,255.85) --
	( 59.75,256.87) --
	( 63.00,257.90) --
	( 66.24,258.95) --
	( 69.48,260.03) --
	( 72.73,261.12) --
	( 75.97,262.24) --
	( 79.22,263.38) --
	( 82.46,264.54) --
	( 85.70,265.72) --
	( 88.95,266.92) --
	( 92.19,268.14) --
	( 95.43,269.38) --
	( 98.68,270.63) --
	(101.92,271.91) --
	(105.17,273.21) --
	(108.41,274.52) --
	(111.65,275.86) --
	(114.90,277.23) --
	(118.14,278.62) --
	(121.39,280.03) --
	(124.63,281.47) --
	(127.87,282.92) --
	(131.12,284.38) --
	(134.36,285.87) --
	(137.61,287.38) --
	(140.85,288.91) --
	(144.09,290.47) --
	(147.34,292.06) --
	(150.58,293.68) --
	(153.82,295.34) --
	(157.07,297.03) --
	(160.31,298.74) --
	(163.56,300.47) --
	(166.80,302.22) --
	(170.04,304.00) --
	(173.29,305.80) --
	(176.53,307.64) --
	(179.78,309.51) --
	(183.02,311.41) --
	(186.26,313.36) --
	(189.51,315.34) --
	(192.75,317.37) --
	(196.00,319.42) --
	(199.24,321.50) --
	(202.48,323.61) --
	(205.73,325.76) --
	(208.97,327.94) --
	(212.21,330.16) --
	(215.46,332.42) --
	(218.70,334.72) --
	(221.95,337.06) --
	(225.19,339.44) --
	(228.43,341.86) --
	(231.68,344.32) --
	(234.92,346.81) --
	(238.17,349.33) --
	(241.41,351.90) --
	(244.65,354.49) --
	(247.90,357.13) --
	(251.14,359.80) --
	(254.39,362.51) --
	(257.63,365.26) --
	(260.87,368.04) --
	(264.12,370.87) --
	(267.36,373.73) --
	(270.60,376.62) --
	(273.85,379.56) --
	(277.09,382.53) --
	(280.34,385.54) --
	(283.58,388.58);
\definecolor{drawColor}{RGB}{86,180,233}

\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 2pt ,line join=round] ( 27.31,247.64) --
	( 30.56,248.47) --
	( 33.80,249.33) --
	( 37.04,250.20) --
	( 40.29,251.09) --
	( 43.53,252.00) --
	( 46.78,252.94) --
	( 50.02,253.89) --
	( 53.26,254.86) --
	( 56.51,255.86) --
	( 59.75,256.87) --
	( 63.00,257.91) --
	( 66.24,258.96) --
	( 69.48,260.04) --
	( 72.73,261.13) --
	( 75.97,262.25) --
	( 79.22,263.39) --
	( 82.46,264.55) --
	( 85.70,265.73) --
	( 88.95,266.93) --
	( 92.19,268.15) --
	( 95.43,269.39) --
	( 98.68,270.65) --
	(101.92,271.92) --
	(105.17,273.22) --
	(108.41,274.54) --
	(111.65,275.88) --
	(114.90,277.24) --
	(118.14,278.63) --
	(121.39,280.04) --
	(124.63,281.48) --
	(127.87,282.92) --
	(131.12,284.39) --
	(134.36,285.87) --
	(137.61,287.38) --
	(140.85,288.91) --
	(144.09,290.47) --
	(147.34,292.05) --
	(150.58,293.67) --
	(153.82,295.33) --
	(157.07,297.02) --
	(160.31,298.73) --
	(163.56,300.45) --
	(166.80,302.20) --
	(170.04,303.97) --
	(173.29,305.78) --
	(176.53,307.61) --
	(179.78,309.47) --
	(183.02,311.38) --
	(186.26,313.32) --
	(189.51,315.31) --
	(192.75,317.33) --
	(196.00,319.38) --
	(199.24,321.47) --
	(202.48,323.58) --
	(205.73,325.73) --
	(208.97,327.92) --
	(212.21,330.14) --
	(215.46,332.40) --
	(218.70,334.70) --
	(221.95,337.05) --
	(225.19,339.44) --
	(228.43,341.86) --
	(231.68,344.33) --
	(234.92,346.82) --
	(238.17,349.36) --
	(241.41,351.93) --
	(244.65,354.54) --
	(247.90,357.18) --
	(251.14,359.87) --
	(254.39,362.59) --
	(257.63,365.35) --
	(260.87,368.14) --
	(264.12,370.98) --
	(267.36,373.85) --
	(270.60,376.76) --
	(273.85,379.71) --
	(277.09,382.70) --
	(280.34,385.72) --
	(283.58,388.79);
\definecolor{drawColor}{RGB}{0,158,115}

\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 4pt ,line join=round] ( 27.31,247.64) --
	( 30.56,248.47) --
	( 33.80,249.32) --
	( 37.04,250.19) --
	( 40.29,251.09) --
	( 43.53,252.00) --
	( 46.78,252.94) --
	( 50.02,253.89) --
	( 53.26,254.86) --
	( 56.51,255.86) --
	( 59.75,256.87) --
	( 63.00,257.91) --
	( 66.24,258.97) --
	( 69.48,260.04) --
	( 72.73,261.14) --
	( 75.97,262.26) --
	( 79.22,263.40) --
	( 82.46,264.56) --
	( 85.70,265.74) --
	( 88.95,266.94) --
	( 92.19,268.16) --
	( 95.43,269.40) --
	( 98.68,270.66) --
	(101.92,271.93) --
	(105.17,273.23) --
	(108.41,274.55) --
	(111.65,275.89) --
	(114.90,277.25) --
	(118.14,278.64) --
	(121.39,280.05) --
	(124.63,281.48) --
	(127.87,282.93) --
	(131.12,284.39) --
	(134.36,285.88) --
	(137.61,287.38) --
	(140.85,288.91) --
	(144.09,290.46) --
	(147.34,292.05) --
	(150.58,293.67) --
	(153.82,295.32) --
	(157.07,297.01) --
	(160.31,298.72) --
	(163.56,300.44) --
	(166.80,302.19) --
	(170.04,303.96) --
	(173.29,305.76) --
	(176.53,307.59) --
	(179.78,309.45) --
	(183.02,311.35) --
	(186.26,313.30) --
	(189.51,315.28) --
	(192.75,317.31) --
	(196.00,319.36) --
	(199.24,321.45) --
	(202.48,323.57) --
	(205.73,325.72) --
	(208.97,327.91) --
	(212.21,330.14) --
	(215.46,332.41) --
	(218.70,334.71) --
	(221.95,337.07) --
	(225.19,339.46) --
	(228.43,341.90) --
	(231.68,344.37) --
	(234.92,346.88) --
	(238.17,349.42) --
	(241.41,352.01) --
	(244.65,354.63) --
	(247.90,357.28) --
	(251.14,359.98) --
	(254.39,362.71) --
	(257.63,365.49) --
	(260.87,368.30) --
	(264.12,371.15) --
	(267.36,374.05) --
	(270.60,376.98) --
	(273.85,379.94) --
	(277.09,382.95) --
	(280.34,385.99) --
	(283.58,389.07);
\definecolor{fillColor}{RGB}{230,159,0}

\path[fill=fillColor] ( 27.31,251.38) --
	( 30.68,245.55) --
	( 23.95,245.55) --
	cycle;

\path[fill=fillColor] ( 35.86,253.72) --
	( 39.22,247.89) --
	( 32.49,247.89) --
	cycle;

\path[fill=fillColor] ( 44.40,256.16) --
	( 47.76,250.34) --
	( 41.03,250.34) --
	cycle;

\path[fill=fillColor] ( 52.94,258.73) --
	( 56.30,252.90) --
	( 49.58,252.90) --
	cycle;

\path[fill=fillColor] ( 61.48,261.41) --
	( 64.85,255.58) --
	( 58.12,255.58) --
	cycle;

\path[fill=fillColor] ( 70.02,264.21) --
	( 73.39,258.38) --
	( 66.66,258.38) --
	cycle;

\path[fill=fillColor] ( 78.57,267.14) --
	( 81.93,261.31) --
	( 75.20,261.31) --
	cycle;

\path[fill=fillColor] ( 87.11,270.19) --
	( 90.47,264.37) --
	( 83.75,264.37) --
	cycle;

\path[fill=fillColor] ( 95.65,273.40) --
	( 99.01,267.58) --
	( 92.29,267.58) --
	cycle;

\path[fill=fillColor] (104.19,276.77) --
	(107.56,270.94) --
	(100.83,270.94) --
	cycle;

\path[fill=fillColor] (112.74,280.26) --
	(116.10,274.43) --
	(109.37,274.43) --
	cycle;

\path[fill=fillColor] (121.28,283.89) --
	(124.64,278.06) --
	(117.91,278.06) --
	cycle;

\path[fill=fillColor] (129.82,287.67) --
	(133.18,281.85) --
	(126.46,281.85) --
	cycle;

\path[fill=fillColor] (138.36,291.63) --
	(141.73,285.80) --
	(135.00,285.80) --
	cycle;

\path[fill=fillColor] (146.90,295.78) --
	(150.27,289.96) --
	(143.54,289.96) --
	cycle;

\path[fill=fillColor] (155.45,300.06) --
	(158.81,294.24) --
	(152.08,294.24) --
	cycle;

\path[fill=fillColor] (163.99,304.54) --
	(167.35,298.72) --
	(160.63,298.72) --
	cycle;

\path[fill=fillColor] (172.53,309.20) --
	(175.89,303.38) --
	(169.17,303.38) --
	cycle;

\path[fill=fillColor] (181.07,314.20) --
	(184.44,308.38) --
	(177.71,308.38) --
	cycle;

\path[fill=fillColor] (189.62,319.33) --
	(192.98,313.51) --
	(186.25,313.51) --
	cycle;

\path[fill=fillColor] (198.16,324.68) --
	(201.52,318.86) --
	(194.79,318.86) --
	cycle;

\path[fill=fillColor] (206.70,330.22) --
	(210.06,324.39) --
	(203.34,324.39) --
	cycle;

\path[fill=fillColor] (215.24,336.05) --
	(218.61,330.22) --
	(211.88,330.22) --
	cycle;

\path[fill=fillColor] (223.78,342.17) --
	(227.15,336.34) --
	(220.42,336.34) --
	cycle;

\path[fill=fillColor] (232.33,348.47) --
	(235.69,342.65) --
	(228.96,342.65) --
	cycle;

\path[fill=fillColor] (240.87,355.10) --
	(244.23,349.27) --
	(237.51,349.27) --
	cycle;

\path[fill=fillColor] (249.41,361.97) --
	(252.77,356.14) --
	(246.05,356.14) --
	cycle;

\path[fill=fillColor] (257.95,369.32) --
	(261.32,363.50) --
	(254.59,363.50) --
	cycle;

\path[fill=fillColor] (266.50,376.85) --
	(269.86,371.02) --
	(263.13,371.02) --
	cycle;

\path[fill=fillColor] (275.04,384.53) --
	(278.40,378.70) --
	(271.67,378.70) --
	cycle;

\path[fill=fillColor] (283.58,392.80) --
	(286.94,386.97) --
	(280.22,386.97) --
	cycle;
\definecolor{fillColor}{RGB}{86,180,233}

\path[fill=fillColor] ( 24.82,245.00) --
	( 29.81,245.00) --
	( 29.81,249.99) --
	( 24.82,249.99) --
	cycle;

\path[fill=fillColor] ( 33.36,247.34) --
	( 38.35,247.34) --
	( 38.35,252.33) --
	( 33.36,252.33) --
	cycle;

\path[fill=fillColor] ( 41.90,249.78) --
	( 46.90,249.78) --
	( 46.90,254.78) --
	( 41.90,254.78) --
	cycle;

\path[fill=fillColor] ( 50.44,252.35) --
	( 55.44,252.35) --
	( 55.44,257.34) --
	( 50.44,257.34) --
	cycle;

\path[fill=fillColor] ( 58.98,255.03) --
	( 63.98,255.03) --
	( 63.98,260.02) --
	( 58.98,260.02) --
	cycle;

\path[fill=fillColor] ( 67.53,257.83) --
	( 72.52,257.83) --
	( 72.52,262.83) --
	( 67.53,262.83) --
	cycle;

\path[fill=fillColor] ( 76.07,260.76) --
	( 81.06,260.76) --
	( 81.06,265.75) --
	( 76.07,265.75) --
	cycle;

\path[fill=fillColor] ( 84.61,263.82) --
	( 89.61,263.82) --
	( 89.61,268.81) --
	( 84.61,268.81) --
	cycle;

\path[fill=fillColor] ( 93.15,267.03) --
	( 98.15,267.03) --
	( 98.15,272.03) --
	( 93.15,272.03) --
	cycle;

\path[fill=fillColor] (101.70,270.41) --
	(106.69,270.41) --
	(106.69,275.40) --
	(101.70,275.40) --
	cycle;

\path[fill=fillColor] (110.24,273.89) --
	(115.23,273.89) --
	(115.23,278.89) --
	(110.24,278.89) --
	cycle;

\path[fill=fillColor] (118.78,277.52) --
	(123.78,277.52) --
	(123.78,282.51) --
	(118.78,282.51) --
	cycle;

\path[fill=fillColor] (127.32,281.30) --
	(132.32,281.30) --
	(132.32,286.30) --
	(127.32,286.30) --
	cycle;

\path[fill=fillColor] (135.86,285.26) --
	(140.86,285.26) --
	(140.86,290.25) --
	(135.86,290.25) --
	cycle;

\path[fill=fillColor] (144.41,289.41) --
	(149.40,289.41) --
	(149.40,294.41) --
	(144.41,294.41) --
	cycle;

\path[fill=fillColor] (152.95,293.67) --
	(157.94,293.67) --
	(157.94,298.67) --
	(152.95,298.67) --
	cycle;

\path[fill=fillColor] (161.49,298.13) --
	(166.49,298.13) --
	(166.49,303.13) --
	(161.49,303.13) --
	cycle;

\path[fill=fillColor] (170.03,302.76) --
	(175.03,302.76) --
	(175.03,307.76) --
	(170.03,307.76) --
	cycle;

\path[fill=fillColor] (178.58,307.80) --
	(183.57,307.80) --
	(183.57,312.80) --
	(178.58,312.80) --
	cycle;

\path[fill=fillColor] (187.12,312.93) --
	(192.11,312.93) --
	(192.11,317.93) --
	(187.12,317.93) --
	cycle;

\path[fill=fillColor] (195.66,318.29) --
	(200.66,318.29) --
	(200.66,323.28) --
	(195.66,323.28) --
	cycle;

\path[fill=fillColor] (204.20,323.80) --
	(209.20,323.80) --
	(209.20,328.79) --
	(204.20,328.79) --
	cycle;

\path[fill=fillColor] (212.74,329.65) --
	(217.74,329.65) --
	(217.74,334.64) --
	(212.74,334.64) --
	cycle;

\path[fill=fillColor] (221.29,335.78) --
	(226.28,335.78) --
	(226.28,340.78) --
	(221.29,340.78) --
	cycle;
